Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation

### 2024-12-04 paper/paper.qmd
Update paper.qmd
update citation

---
title: "Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation"
author: 
  - Liu Zilin
thanks: "Code and data are available at: [https://github.com/zilin1017/King-Street-Traffic-Pilot-Project](https://github.com/zilin1017/King-Street-Traffic-Pilot-Project)."
date: "December 1, 2024"
date-format: long
abstract: "The paper provides a detailed analysis of the King Street transport pilot project, which aims to assess the impact of prioritizing trams over private cars on transport reliability, speed and capacity. Through the modeling and improvement of traffic data, the study gradually optimized the model variables and found that the model after logarithmic transformation performed best, with R-Square = 0.6345, which significantly improved the explanatory power of traffic flow changes. The pilot policy has achieved significant results in reducing traffic pressure at specific intersections and reducing interference from private cars. The effect of the policy is particularly significant on road sections with heavy traffic and during peak hours. In addition, the impact of different time periods and intersection characteristics on traffic patterns shows complex dynamic characteristics, which further indicates that targeted adjustment of traffic signals and optimization of priority policy implementation strategies will help further improve policy effects."
format: pdf
number-sections: true
bibliography: references.bib
citeproc: true
---
# Introduction

@@

After introducing the source and background of the data, here we will explain how to use the `R` language [@citeR] functions and some additional packages learned in the course to process the data. Here is a unified overview. The `dplyr` package [@dplyr] is a grammar of data manipulation, providing a consistent set of verbs that help us solve the most common data manipulation challenges. In this package, this article mainly uses the `mutate` function and the `filter`function, where the `mutate`[@dplyrMutate] function creates new columns that are functions of existing variables. The `filter` [@dplyrFilter] function is used to subset a data frame, retaining all rows that satisfy conditions.In the visualization stage, this article uses the `ggplot`[@ggplot2] package to draw graphics, and when analyzing the results, in order to see the output results more intuitively, this article also uses the `xtable`[@xtable] package to convert the results into `LaTex` format for output. Finally, in order to output the variable data that needs to be analyzed, this article also draws on the `arrow`[@arrow] package recommended in the course to output data in `parquet` format. Also this analysis inherits the folder structure from Professor Rohan Alexander from University of Toronto [@Rohan].

>>>>

---
title: "Analysis of the King Street Traffic Pilot Project on Improving the Reliability, Speed, and Capacity of Transportation"
subtitle: “Assessing the Impact of Tram Prioritization on Urban Traffic Efficiency”
author: 
  - Irene Liu
thanks: "Code and data are available at: [https://github.com/zilin1017/King-Street-Traffic-Pilot-Project](https://github.com/zilin1017/King-Street-Traffic-Pilot-Project)."
date: today
date-format: long
abstract: "The paper provides a detailed analysis of the King Street transport pilot project, which aims to assess the impact of prioritizing trams over private cars on transport reliability, speed and capacity. Through the modeling and improvement of traffic data, the study gradually optimized the model variables and found that the model after logarithmic transformation performed best, with R-Square = 0.6345, which significantly improved the explanatory power of traffic flow changes. The pilot policy has achieved significant results in reducing traffic pressure at specific intersections and reducing interference from private cars. The effect of the policy is particularly significant on road sections with heavy traffic and during peak hours. In addition, the impact of different time periods and intersection characteristics on traffic patterns shows complex dynamic characteristics, which further indicates that targeted adjustment of traffic signals and optimization of priority policy implementation strategies will help further improve policy effects."
format: pdf
number-sections: true
bibliography: references.bib
citeproc: true
---
# Introduction

@@

After introducing the source and background of the data, here we will explain how to use the `R` language [@citeR] functions and some additional packages learned in the course to process the data. Here is a unified overview. The `dplyr` package [@dplyr] is a grammar of data manipulation, providing a consistent set of verbs that help us solve the most common data manipulation challenges. In this package, this article mainly uses the `mutate` function and the `filter`function, where the `mutate`[@dplyrMutate] function creates new columns that are functions of existing variables. The `filter` [@dplyrFilter] function is used to subset a data frame, retaining all rows that satisfy conditions.In the visualization stage, this article uses the `ggplot`[@ggplot2] package to draw graphics, and when analyzing the results, in order to see the output results more intuitively, this article also uses the `xtable`[@xtable] package to convert the results into `LaTex` format for output. Finally, in order to output the variable data that needs to be analyzed, this article also draws on the `arrow`[@arrow] package recommended in the course to output data in `parquet` format, and other Key libraries that supported the data analysis include `readxl`[@readxl], `ggbeeswarm`[@ggbeeswarm]. Also this analysis inherits the folder structure from Professor Rohan Alexander from University of Toronto [@Rohan].
